---
title: "Assessment 1.1"
author: "Hsin-Chieh Tang s4647300"
date: "14/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# RMarkdown **_editing_**

**R Markdown** is a file format that is used in Rstudio to produce dynamic documents, which contains Markdown and R code. It creates an easy way for writing by using plain text format, and simply reading through common output format such as *html*.

[link](https://rmarkdown.rstudio.com/lesson-8.html)


### **Part 1**

Create a variable with the dataset.

```{r}
# install.packages("tidyverse")

library(tidyverse)

fastfood <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv')

```
Display the first 10 rows of the dataset.

```{r}
library(tidyverse)

fastfood%>%head(10)
```
Display the first 10 rows of the dataset and the first 5 variables using kabble() function.

```{r}
# install.packages("knitr")

library(knitr)

knitr::kable(head(fastfood[, 1:5]), "pipe")
```
Display the observations that has more than 1000 calories.

```{r}
filter(fastfood, calories>1000)
```
Save observations with more than 40 in total_fat and more than 80 in total_carb in a new variable called `dont_eat_this`.

```{r}
fastfood %>% filter(total_fat> 40 & total_carb> 80)

dont_eat_this <-fastfood %>% filter(total_fat> 40 & total_carb> 80)
```
Display observations from restaurant Mcdonalds.
```{r}
fastfood %>% filter(restaurant=="Mcdonalds")
```

### **Part 2**

Display the types of variables in the dataset.

```{r}
library(skimr)

fastfood%>%skim()
```

Show the count of observations for each restaurant.

```{r}
fastfood%>%count(restaurant)
```
Summarise and display the average number of calories for each restaurant.
```{r}
fastfood%>%
  group_by(restaurant)%>%
  summarise(calories=mean(calories))
```
Add a variable to the dataset, which calculates the average calories per type of restaurant and call it `average_calories`.
```{r}
# install.packages("dplyr")

library(dplyr)

fastfood %>%
  group_by(restaurant) %>% 
  summarise(average_calories = mean(calories)) %>% 
  mutate(average_calories)
```
### Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best.
```{r}

# install.packages("scales")
# install.packages("lubridate")

library(tidyverse)
library(scales)
library(lubridate)



```
### Add a variable to the dataset, which calculates the maximum total fat per type of restaurant and call it `max_total_fat`.
```{r}

max_total_fat <- 
  fastfood %>% 
  group_by(restaurant) %>%
  summarise(total_fat)
  

```
### Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()`.
```{r}



```

### **Part 3**

Identify variable(s) which should be factors and transform their type into a factor variable.
```{r}


```

Create two new variables
```{r}



```

